
\input{parts/config.tex}
\input{parts/header_footer_en.tex}

\begin{document}

\input{parts/title_en.tex}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------


\begin{minipage}[t]{0.55\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages

  \cvsect{BRIEFLY ABOUT ME}

	Developer with over 10 years of experience.
  \bigskip
  \small{
    \begin{itemize}[leftmargin=1pt]
      \item In my last years of university, I worked as a C\# developer.
      \item After that, I worked as a "development department" in a small family company (PHP, JS, CSS).
      \item Then, for some time I was engaged in SEO (website promotion in search engines) and taught it, combining it with freelance website development.
      \item Currently, I work as an outsource developer in a wholesale company (PHP, JS, SCSS).
      \item{Main technologies used: PHP, SCSS, JS (mainly jQuery), Docker, Yarn, Composer, Gulp, Git (GitHub), Webpack (implemented recently).}
      \item Occasionally used: Python, rarely C\#.
      \item Hired freelancers at various times.
      \item Now 1 programmer is subordinate.
    \end{itemize}
  }
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.35\textwidth} % 50% of the page for the skills bar chart
	 \vspace{-\baselineskip} % Required for vertically aligning minipages

   \input{parts/skills.tex}
\end{minipage}

% \begin{center}
% 	\bubbles{5/PHPStorm, 4/Linux DE, 3/Linux Server, 5/Windows}
% \end{center}



%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{EXPERIENCE}

\begin{entrylist}
	\entry
		{2/2018 -- present}
		{Full-stack outsource}
		{ООО "'Интерьер комфорт"' }
		{Since 2018 I work for the company full time as the only developer. Since the beginning of 2021, I got 1 programmer as a subordinate.

    What I do/did:
    \begin{itemize}
      \item Development of a new warehouses and wholesales system from scratch. Development of an internal CMS for this system. \underline{Architecture, frontend, backend, database.}
      \item Transferring an online store to that CMS.
      \item Allocation of that CMS core in a separate project (framework).
      \item Development of a transportation management system (transport company) based on the developed framework.
    \end{itemize}

		\texttt{PHP}\slashsep\texttt{JS}\slashsep\texttt{SCSS}\slashsep\texttt{MySQL}\slashsep\texttt{Linux}
    \slashsep\texttt{Docker}\slashsep\texttt{Yarn/NPM}\slashsep\texttt{Composer}\slashsep\texttt{GitHub}

    \texttt{Gulp}\slashsep\texttt{Webpack}}

	\entry
		{3/2016 -- 2/2018

		\footnotesize{part-time}}
		{Full-stack outsource}
		{ООО "'Интерьер комфорт"' }
		{
    \begin{itemize}
      \item Servers maintenance.
      \item Development of new functionality and support of 2 online stores.
      \item Support and maintenance of "warehouse and wholesale management system", which I developed earlier as a freelancer.
      \item Adding new features to that system
    \end{itemize}

		\texttt{PHP}\slashsep\texttt{JS}\slashsep\texttt{SCSS}\slashsep\texttt{MySQL}\slashsep\texttt{Linux}
    \slashsep\texttt{Yarn/NPM}\slashsep\texttt{Composer}\slashsep\texttt{GitHub}\slashsep\texttt{Gulp}
    }

	\entry
		{3/2015 -- 4/2017

		\footnotesize{part-time}}
		{SEO teacher}
		{ООО "'ТопЭксперт"' (www.topexpert.pro)}
		{Taught basic knowledge of Search Engine Optimization (SEO) on the educational platform called TopExpert. Conducted a total of 7 study groups (more than 100 people).

    The lecture's main emphasis was what a search engine is and how it works, what mistakes (in terms of SEO) site developers make and how to fix them. Wrote a guide about compiling the semantic core of the site.

    Duties included:
    \begin{itemize}
      \item conducting theoretical and practice lessons
      \item checking homework assignments
      \item development of the training plan and the course itself
      \item creating additional materials (presentations, examples, etc.)
    \end{itemize}
    }

	\entry
		{4/2013 -- 2/2018

		\footnotesize{part-time}}
		{SEO specialist/Full-stack PHP dev}
		{Freelance}
    {Since the end of 2013, I, little by little, began to provide SEO services. Since 2015, SEO orders have been the majority of orders. The focus was on features that can be implemented from the developer's side. Those that almost no one thinks about at the development stage.\\
    I continued to develop websites, but in smaller numbers (up to 10 websites per year). I mainly made websites using AmiroCMS and, sometimes, 1C Bitrix, WordPress, OpenCart.

		\texttt{PHP}\slashsep\texttt{JS}\slashsep\texttt{CSS}\slashsep\texttt{MySQL}\slashsep\texttt{Linux}}

  \entry
    {2009 -- 2015}
    {Full-stack PHP dev}
    {www.evrosite.ru}
    {I was working for a small family company as a single developer. From time to time, freelancers were involved in the work, to whom I distributed tasks and checked the quality of execution.

    I was in charge of the entire cycle of website development, from layout to placement on a hosting/server (including server support). Development was done, mostly, on the internal CMS developed by the previous programmer. Also, other CMS was used, such as OpenCart, 1C Bitrix, AmiroCMS, WordPress. In difficult times, I also performed the work of a salesman, project manager, and other duties.

    \texttt{PHP}\slashsep\texttt{JS}\slashsep\texttt{CSS}\slashsep\texttt{MySQL}\slashsep\texttt{Linux}}

	\entry
		{2007 -- 2008

		\footnotesize{part-time}}
		{Junior C\# Developer}
		{ООО 'Группа Алланд'}
		{We developed information systems with specific tasks. Such as monitoring the full cycle of holding all-Russian intellectual competitions for schoolchildren.\\
    My duties were:
    \begin{itemize}
      \item development of UI
      \item testing UI
      \item writing some simple controllers and data layers
      \item system architecture and database architecture (to a much lesser extent)
    \end{itemize}

		\texttt{C\#}\slashsep\texttt{SQL}\slashsep\texttt{Web/WinServices}\slashsep\texttt{OLAP}\slashsep\texttt{TFS}}

\end{entrylist}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{EDUCATION}

\begin{entrylist}
	\entry
		{2003 -- 2008\\\footnotesize{Bachelor's degree\\full-time education}}
		{Math. support and administration of information systems}
		{Ulyanovsk State University}
		{I received a diploma of higher education in the specialty 'Mathematical support and administration of information systems' at Ulyanovsk State University.

    Diploma topic: Development of an automated user support system based on an embedded Internet pager (.NET).

    Technologies: C\#, MSSQL, Client-Server
		}
	\entry
		{constant}
		{self-education}
		{}
		{I try to learn new technologies and improve my knowledge of existing ones. I occasionally try machine learning. I went through tutorials on ReactJS and Go. I listened to lectures on functional programming and Haskel in particular. Unfortunately, it is difficult to study something that is not applicable at the moment, since there is nowhere to apply it.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}

	\textbf{Russian} - native\\
	\textbf{English} - speak/write\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Hobby}

  I often watch something educational. I study different things, mostly related to computers. For example, Pen-testing or 3d modeling.
  Less often - I read sci-fi and fantasy.

\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Non profit}

	Occasionally I write something in the blog and answer on StackOverflow. Sometimes I review posts on StackOverflow.
\end{minipage}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\end{document}
